---
title: New Paper
running-head: New paper
author: 
  - name: Sam Harper
    orcid: 0000-0002-2767-1053
    email: sam.harper@mcgill.ca
    corresponding: true
    affiliation: 
      - ref: 1
affiliations:
  - id: 1
    name: McGill University
    department: Department of Epidemiology
abstract: |
  Why did we start? Because chocolate. What did we do? Ate chocolate. What did we find? It’s delicious. What does it all matter? It's obvious!
keywords: [heterogeneity, uncertainty, variation, multilevel model, statistics, visualization]
authornote: |
  This manuscript is not yet peer-reviewed.
bibliography: np.bib
citeproc: true
csl: vancouver.csl
---


```{r}
#| label: setup
#| include: false

# Packages
library(here)
library(tidyverse)
library(tinytable)
library(modelsummary)
library(marginaleffects)
library(knitr)


# Output options
is_html <- knitr::is_html_output()
opts_chunk$set(
 eval = TRUE,
 cache = TRUE,
 warning = FALSE,
 error = FALSE,
 message = FALSE,
 echo = is_html
)
options(digits = 2)
options(tinytable_tt_digits = 2)

# Plotting options
plot_font <- ifelse(is_html, "Fira Sans", "Libertinus Sans")
update_geom_defaults("text", list(family = plot_font))
theme_set(
  theme_classic(base_size = 10, base_family = plot_font) +
    theme(
      strip.text = element_text(color = "black", hjust = 0),
      strip.background = element_rect(color = NA, fill = NA),
      strip.text.x = element_text(size = rel(0.9)),
      line = element_line(linewidth = .25),
      plot.tag = element_text(size = rel(1)),
      plot.tag.location = "margin"
    )
)

```

# Background

Let’s face it. Chocolate is delicious, and it seems impossible that it might not be good for you. However, the science is unclear, at least for some outcomes.[@chan2007]

# Methods

We recruited students who thought they were coming for training in reproducible research methods as a pre-text for eating chocolate in the morning. We measured their happiness using our established, validated index.

We calculated some descriptive statistics and ran a simple linear regression model, shown in @eq-1:

$$
y_{it}=\beta_{0} + \beta_{1}*Treated + \beta_{2}*Period + \epsilon_{it}
$$ {#eq-1}

We also explored a model with a product term, but not because p>0.05 in the previous model. Honest.

# Results

Descriptive statistics are shown in Table 1

```{r table1}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
#| tbl-cap: Mean happiness by treatment and time

# read in the raw data
d <- read_csv(here("data-source", 
  "choc-data-raw-r.csv")) %>%
  # create factors for period and treatment
  mutate(
    period = factor(period, levels=c(0,1,2), 
      labels=c("Pre", "Intervention", "Post")),
    treated = factor(treated, levels=c(0,1), 
      labels=c("Control", "Treated")))

# summarize means and SDs for table 1
t1 <- d %>%
  group_by(period, treated) %>%
  summarise(
    meany = mean(y),
    sdy = sd(y)
  )

# column names for the table
colnames(t1) <- c("Period", "Treatment", "Mean", "SD")

# print the table
tt(t1, digits=2) %>% 
  style_tt(i=c(1,3,5), j=1, rowspan=2)
```

Estimates from the regression analysis are shown in Table 2. Regression results clearly show that chocolate increases happiness. We can see that the overall happiness index for the chocolate group was 4.67 units higher in the post period relative to the change over the same period in the control group [95% CI: 3.66, 5.68].

```{r t2}
#| echo: FALSE
#| tbl-cap: Regression results

# run the regression models
t2c <- lm(y ~ treated + period, data=d)
t2i <- lm(y ~ treated * period, data=d)

modelsummary(list(t2c,t2i))
```

Regression results clearly show that chocolate increases happiness, but if you aren't convinced please see Figure 1.

```{r figure1}
#| echo: FALSE
#| fig-cap: Predicted happiness index from interaction model.

# plot the predicted values
marginaleffects::plot_predictions(t2i, 
  condition=c("period", "treated"))
```

# Discussion

We think this is convincing. But it may not matter for policy since another randomized trial showed that many participants switched groups mid-study because of their personal chocolate preferences.[@scaramuzza2015]

# References

